Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-06-16 manuscript.qmd
minor corrections, adding unit in plots, computing median efficacy, ...

---
title: "Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application"
author: 
  - "Armand Favrot"
  - "Sophie Génermont"
  - "Céline Decuq"
  - "Jean-Marc Giliot"
  - "David Makowski"
format:
  html:
    toc: true
    embed-resources: true
---

@@

    ggplot () +
        geom_line (aes (x = time, y = e.rel, group = pmid), linewidth = 0.15) +
        ylab ("Cumul of relative emission") +
        xlab ("Time (h)") +
        theme (axis.title.y = element_text (margin = ggplot2::margin (r = 25)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0))) +
        # scale_color_manual (values = Dark2) +
        facet_wrap (~ strategy)

@@

```{r, fig.height = 12, fig.width = 10}
plot_residuals_complete_dataset = predictions_of_all_methods %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method)) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

```{r, fig.height = 12, fig.width = 10}
plot_residuals_evaluation_subset = predictions_of_all_methods %>%
    filter (dataset == "Evaluation subset") %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method), varwidth = TRUE) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

        xlab ("Observed values") + ylab ("Predicted values") +

@@

```{r, fig.width = 20, fig.height= 8}
data_tmp = data_scenarios %>%
    filter (efficacy_xgboost > 0) %>%
    select (efficacy_xgboost, tan.app, app.mthd, app.rate, man.source, incorp, group_temp, group_wind, group_rain) %>%
    mutate (group_rain = ifelse (group_rain == "q1", "low", "high")) %>%
    mutate (tan.app = paste ("TAN = ", tan.app),
            app.rate = paste ("Application rate = ", app.rate),
            group_rain = paste ("Rain = ", group_rain))

plot = ggplot (data_tmp) +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate + group_rain) +
    xlab ("Efficacy") +
    ylab ("Number of predictions") +
    theme (axis.title.y = element_text (margin = ggplot2::margin (r = 20)),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)),
           strip.text = element_text (size = 24))

@@

>>>>

---
title: "Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application"
author: 
  - "Armand Favrot"
  - "Sophie Génermont"
  - "Céline Decuq"
  - "David Makowski"
format:
  html:
    toc: true
    embed-resources: true
---

@@

    ggplot () +
        geom_line (aes (x = time, y = e.rel, group = pmid), linewidth = 0.15) +
        ylab ("Cumulative emission (frac. applied TAN)") +
        xlab ("Time (h)") +
        theme (axis.title.y = element_text (margin = ggplot2::margin (r = 25)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0))) +
        # scale_color_manual (values = Dark2) +
        facet_wrap (~ strategy)

@@

```{r, fig.height = 12, fig.width = 10}
plot_residuals_complete_dataset = predictions_of_all_methods %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method)) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual (frac. applied TAN)") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

```{r, fig.height = 12, fig.width = 10}
plot_residuals_evaluation_subset = predictions_of_all_methods %>%
    filter (dataset == "Evaluation subset") %>%
    mutate (residuals = truth_er - er) %>%
    mutate (app.mthd = recode (app.mthd, "bc" = "Broadcast", "bsth" = "Trailing hose", "ts" = "Trailing shoe", "os" = "Open slot injection")) %>%
    mutate (app.mthd = factor (app.mthd, levels = c ("Broadcast", "Trailing hose", "Trailing shoe", "Open slot injection"))) %>%
    ggplot () +
        geom_boxplot (aes (x = country, y = residuals, fill = method), varwidth = TRUE) +
        geom_hline (yintercept = 0, linetype = 2) +
        scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
        facet_wrap (~ app.mthd, ncol = 1) +
        ylab ("Residual (frac. applied TAN)") +
        labs (fill = "") +
        theme (legend.position = "bottom",
               axis.title.y = element_text (margin = ggplot2::margin (r = 30)),
               strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)))

@@

        xlab ("Observed values (kg/ha)") + ylab ("Predicted values (kg/ha)") +

@@

```{r, fig.width = 20, fig.height= 8}
data_tmp = data_scenarios %>%
    filter (efficacy_xgboost > 0) %>%
    select (efficacy_xgboost, tan.app, app.mthd, app.rate, man.source, incorp, group_temp, group_wind, group_rain) %>%
    mutate (group_rain = ifelse (group_rain == "q1", "low", "high")) %>%
    mutate (tan.app = paste ("TAN = ", round (tan.app, digits = 1), " kg/ha", sep = ""),
            app.rate = paste ("Application rate = ", round (app.rate, digits = 1), " t/ha or m3/ha", sep = ""),
            group_rain = paste ("Rain = ", group_rain))

plot = ggplot (data_tmp) +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate + group_rain) +
    xlab ("Efficacy") +
    ylab ("Number of predictions") +
    theme (axis.title.y = element_text (margin = ggplot2::margin (r = 20), size = 18),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)),
           strip.text = element_text (size = 18),
           axis.text = element_text (size = 18),
           axis.title.x = element_text (size = 18))

@@

```{r}
data_scenarios %>%
  filter (! (app.mthd == "bc" & incorp == "none")) %>%
  summarise (median_rf = median (efficacy_random_forest), 
             median_alfam2 = median (efficacy_alfam2), 
             median_gbf = median (efficacy_xgboost), 
             median_lasso = median (efficacy_lasso), .by = c ('app.mthd')) %>%
  mutate_if (is.numeric, round, digits = 1) %>%
  kable()
```
